Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-22 paper/paper.tex
proper citation in the intro

% general intro text with motivation
Deep neural networks are an integral part of machine learning and data science toolset
for practical data-driven problem solving. With continual miniaturization ever more
applications can be found in embedded systems. Common embedded applications include
on-device image recognition and signal processing. Despite recent advances in generalization
and optimization theory specific to deep networks, deploying in actual embedded hardware
remains a challenge due to storage, real-time throughput, and numerical computational
complexity restrictions. Therefore compression methods for achieving high model sparsity
and numerical efficiency without losing much in performance are especially relevant.
% Solving the storage and compute constraints encourages development of model compression
% and sparsification methods, that focus on favourable tradeoff between performance and size.

>>>>

% general intro text with motivation
Deep neural networks are an integral part of machine learning and data science toolset
for practical data-driven problem solving. With continual miniaturization ever more
applications can be found in embedded systems. Common embedded applications include
on-device image recognition and signal processing. Despite recent advances in generalization
and optimization theory specific to deep networks, deploying in actual embedded hardware
remains a challenge due to storage, real-time throughput, and numerical computational
complexity restrictions \citep{he_amc:_2018}. Therefore compression methods for achieving
high model sparsity and numerical efficiency without losing much in performance are
especially relevant.
% Solving the storage and compute constraints encourages development of model compression
% and sparsification methods, that focus on favourable tradeoff between performance and size.
